---
title: "One Command Line Plot - The Rest"
author: "Walter Xie"
date: "09/02/2017"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

One of the feature of [**ComMA**](http://github.com/walterxie/ComMA) package is to simplify [ggplot2](http://docs.ggplot2.org/current/) codes into one-line functions, and also to provide some other useful utility functions.

```{r library, warning=FALSE}
library(ComMA)
#getwd()
```

## Box Whiskers plot

Load the example data *model.test*, and display the first 3 rows:

```{r model.test}
data(model.test)
model.test[1:3,]
```

Plot the performance score of each test in four GTR models, where the texts of x-axis were rotated, and also use <code>verbose=F</code> to block messages:

```{r BoxWhiskersPlot1, warning=FALSE}
ggBoxWhiskersPlot(model.test, x.id="test", y.id="performance", colour.id="OS", x.text.angle=90, verbose = F)
```

### Adjust view

Zoom the plot without change the underlying data

```{r BoxWhiskersPlot2, warning=FALSE}
# Zoom the plot without change the underlying data
ggBoxWhiskersPlot(model.test, x.id="test", y.id="performance", colour.id="OS", 
                  x.text.angle=90, y.lim.cart=c(NA,5), verbose = F)
```

Use both <code>bar.pos="fill"</code> and <code>y.trans="per"</code> to create a typical percentage bar chart:

```{r BoxWhiskersPlot3, warning=FALSE}
ggBoxWhiskersPlot(model.test, x.id="test", y.id="performance", colour.id="OS", 
                  x.text.angle=90, y.lim.cart=c(NA,5), verbose = F)
```


## Histogram

This plots a 1d distribution by dividing "performance" into bins and counting the number of observations in each bin.

```{r Histogram, warning=FALSE}
ggHistogram(model.test[model.test$performance<3,], x.id="performance", fill.id="model", 
            binwidth=0.1, x.text.angle=90, verbose=F)
```


## Heatmap



## Kernel density estimate




